% ----------------------------------------------------------------------
\begin{frame}[fragile,shrink]{Hamiltonian cycle}{Instance}
  \bigskip
  \begin{columns}
    \begin{column}{0.4\textwidth}
      \begin{minipage}{.4\textwidth}
      \begin{semiverbatim}
{\color{comment}\% vertices}
node(a).  node(b).
node(c).  node(d).

{\color{comment}\% edges}
edge(a,b).  edge(a,c).
edge(b,c).  edge(b,d).
edge(c,a).  edge(c,d).
edge(d,a).

{\color{comment}\% starting point}
start(a).
      \end{semiverbatim}
    \end{minipage}
    \end{column}
    \begin{column}{0.4\textwidth}
      \centering
      \Graph
    \end{column}
  \end{columns}
\end{frame}
% ----------------------------------------------------------------------
\begin{frame}[fragile,shrink]{Hamiltonian cycle}{Encoding}
\begin{SemiVerbatim}[\small]{.9}
{\color{comment}\% generate path}
path(X,Y) :- not omit(X,Y), edge(X,Y).
omit(X,Y) :- not path(X,Y), edge(X,Y).

{\color{comment}\% at most one incoming/outgoing edge}
:- path(X,Y), path(X',Y), X < X'.
:- path(X,Y), path(X,Y'), Y < Y'.

{\color{comment}\% at least one incoming/outgoing edge}
on_path(Y) :- path(X,Y), path(Y,Z).
:- node(X), not on_path(X).

{\color{comment}\% connectedness}
reach(X) :- start(X).
reach(Y) :- reach(X), path(X,Y).
:- node(X), not reach(X).
\end{SemiVerbatim}
\end{frame}
% ----------------------------------------------------------------------
\begin{frame}{Essential concepts}
  \begin{itemize}
    \item \structure{Safety} \ of a rule
      \begin{itemize}
        \item each variable must occur in a positive body literal
      \end{itemize}
    \item \structure{Term universe} \ of a program
      \begin{itemize}
        \item
          all constants in the program
      \end{itemize}
    \item \structure{Atom base} \ of a program
      \begin{itemize}
        \item all ground atoms over predicates in program
      \end{itemize}
    \item \structure{Ground instance} \ of a rule
      \begin{itemize}
        \item all variables replaced with elements from term universe
      \end{itemize}
    \item \structure{Ground instantiation} \ of a logic program
      \begin{itemize}
        \item \(\ground{P}\) is the union of all instances of % all
              rules in \(P\)
      \end{itemize}
    \item \structure{Unifier} \ of two expressions
      \begin{itemize}
      \item a (variable) substitution making two expressions equal\\ once applied to both
      \end{itemize}
  \end{itemize}
\end{frame}
% ----------------------------------------------------------------------
\begin{frame}[fragile,shrink]{Size of grounding}{Hamiltonian cycle}
  \begin{SemiVerbatim}{.9}
{\color{comment}\% term universe: \{a,b,c,d\}}
12 facts from instance
{\color{comment}\% path(X,Y) :- not omit(X,Y), edge(X,Y).}
{\color{comment}\% omit(X,Y) :- not path(X,Y), edge(X,Y).}
{\color{comment}\% reach(Y) :- reach(X), path(X,Y).}
16 rules + 16 rules + 16 rules
{\color{comment}\% on_path(Y) :- path(X,Y), path(Y,Z).}
{\color{comment}\% :- path(X,Y), path(X',Y), X < X'.}
{\color{comment}\% :- path(X,Y), path(X,Y'), Y < Y'.}
64 rules + 64 rules + 64 rules
{\color{comment}\% reach(X) :- start(X).}
{\color{comment}\% :- node(X), not on_path(X).}
{\color{comment}\% :- node(X), not reach(X).}
4 rules + 4 rules + 4 rules
  \end{SemiVerbatim}
\end{frame}
% ----------------------------------------------------------------------
\begin{frame}[fragile,shrink]{Unnecessary rules, I}{Hamiltonian cycle}
  \bigskip
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \begin{minipage}{0.6\textwidth}\small
      \begin{semiverbatim}
{\color{comment}\% path(X,Y) :- not omit(X,Y), edge(X,Y).}
path(a,a) :- not omit(a,a), \alert{edge(a,a)}.
path(a,b) :- not omit(a,b), edge(a,b).
path(a,c) :- not omit(a,c), edge(a,c).
path(a,d) :- not omit(a,d), \alert{edge(a,d)}.
          \(\vdots\)
path(d,a) :- not omit(d,a), edge(d,a).
path(d,b) :- not omit(d,b), \alert{edge(d,b).}
path(d,c) :- not omit(d,c), \alert{edge(d,c).}
path(d,d) :- not omit(d,d), \alert{edge(d,d).}

      \end{semiverbatim}
    \end{minipage}
    \end{column}
    \begin{column}{0.25\textwidth}
      \Graph
    \end{column}
  \end{columns}
\end{frame}
% ----------------------------------------------------------------------
\begin{frame}[fragile,shrink]{Unnecessary rules, II}{Hamiltonian cycle}
  \bigskip
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \begin{minipage}{0.6\textwidth}\small
      \begin{semiverbatim}
{\color{comment}\% :- path(X,Y), path(X',Y), X < X'.}
:- \alert{path(a,a)}, \alert{path(a,a)}, \alert{a < a}.
:- path(a,b), path(a,b), \alert{a < a}.
:- path(a,c), path(a,c), \alert{a < a}.
:- \alert{path(a,d)}, \alert{path(a,d)}, \alert{a < a}.

:- \alert{path(a,a)}, \alert{path(b,a)}, a < b.
:- path(a,b), \alert{path(b,b)}, a < b.
:- path(a,c), path(b,c), a < b.
:- \alert{path(a,d)}, path(b,d), a < b.
          \(\vdots\)
:- \alert{path(d,d)}, \alert{path(d,d)}, \alert{d < d}.
      \end{semiverbatim}
    \end{minipage}
    \end{column}
    \begin{column}{0.25\textwidth}
      \Graph
    \end{column}
  \end{columns}
\end{frame}
% ----------------------------------------------------------------------
%
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../main"
%%% End:
