% ----------------------------------------------------------------------
\begin{frame}{Propagation of\only<2->{ true} atoms}
  \bigskip
  \begin{itemize}
  \item Simplifications are performed \alert{on-the-fly} relative to the atom base
    \begin{itemize}\normalsize
    \item [\itarrow] rules are printed immediately but not stored in \gringo
    \end{itemize}
    \medskip
  \item<2-> Distinguish a set of \alert{true atoms} among the atom base
    \begin{itemize}\normalsize
    \item [\itarrow] each true atom amounts to a fact
    \end{itemize}
    \medskip
  \item<3-> \structure{Simplifications}
    \begin{itemize}\normalsize
    \item Remove facts from positive body
      \smallskip
    \item Discard rules with negative literals over a fact
      \smallskip
    \item Discard rules whenever the head is a fact
      \smallskip
    \item Gather new facts whenever a rule body is empty
    \end{itemize}
  \end{itemize}
\end{frame}
% ----------------------------------------------------------------------
\begin{frame}[fragile]{Propagation of true atoms}{Hamiltonian cycle}
  \bigskip
  \begin{SemiVerbatim}{.9}
...
path(a,b) :- not omit(a,b)\only<1>{, \alert{edge(a,b)}}.
...
reach(a)\only<1>{ :- \alert{start(a)}}. {\only<2->{\color{comment}\% reach(a) is added as fact}}
\visible<3->{
...

\only<4>{\sout}{{:- node(a), not \alert{reach(a)}}.} {\only<4->{\color{comment}\% rule is discarded}}
...}
\end{SemiVerbatim}
\end{frame}
% ----------------------------------------------------------------------
\begin{frame}{Propagation of false atoms}
  \bigskip
  \begin{itemize}
  \item<2-> \alert{Non-recursive body negative literals} whose atom is not in the
    \\ current atom base can be removed from rule bodies
    \medskip
  \item<3-> \structure{Example} \ Consider the instance where node \texttt{d} is not reachable
  \bigskip
  \begin{center}
    \Graph[draw=none]
  \end{center}
  \end{itemize}
\end{frame}
% ----------------------------------------------------------------------
\begin{frame}[fragile,shrink]{Propagation of negative literals}{Hamiltonian cycle}
  \medskip
  \begin{columns}
    \begin{column}{0.45\textwidth}
    \begin{minipage}{.4\textwidth}\small
      \begin{semiverbatim}
path(a,b) :- not omit(a,b).
path(a,c) :- not omit(a,c).
path(b,c) :- not omit(b,c).
path(c,a) :- not omit(c,a).
path(d,a) :- not omit(d,a).
...
\alert{reach(a)}.
\alert{reach(b)} :- path(a,b).
\alert{reach(c)} :- path(a,c).
\alert{reach(c)} :- path(b,c), reach(b).
...
\mbox{{\color{comment}\% reach(d)\({}\not\in{}D\) (atom base)}}
:- not reach(b).
:- not reach(c).
:- \only<1>{not \alert{reach(d)}}. \color{comment}\% \alt<2>{inconsistency detected during grounding}{remove not reach(d) from body}
      \end{semiverbatim}
    \end{minipage}
    \end{column}
    \begin{column}[t]{0.45\textwidth}
      \centering
      \Graph[draw=none]
    \end{column}
  \end{columns}
\end{frame}
% ----------------------------------------------------------------------
\begin{frame}{Stratified logic programs}
  \bigskip
  \begin{itemize}
  \item<only@2-5> The \alert{definition} of a predicate $p$ in a program $P$, written $\mathit{def}_P(p)$,
    \\
    is the subset of $P$ consisting of all rules with $p$ in the head
    \medskip
  \item<3-> A logic program $P$ is \alert{stratified}, if
    \alt<6>{its dependency graph has no cycles containing negative edges}
    {it has a partition
    \(
    (P_i)_{0\leq i\leq n}
    \)

    such that for each predicate $p$
    \begin{itemize}\normalsize
    \item $\mathit{def}_P(p)\subseteq P_i$ for some $1\leq i\leq n$
    \end{itemize}
    and, for each $1\leq i\leq n$,
    \begin{itemize}\normalsize
    \item if $p$ occurs in \pbody{r} for some $r\in P_i$, then $\mathit{def}_P(p)\subseteq\bigcup_{j\leq i} P_j$
    \item if $p$ occurs in \nbody{r} for some $r\in P_i$, then $\mathit{def}_P(p)\subseteq\bigcup_{j  <  i} P_j$
    \end{itemize}}
  \medskip
  \item<4-> \structure{Property} \
    Stratified logic programs
    \begin{itemize}\normalsize
    \item are \alert{completely evaluated} during grounding
    \item <5-> have a single stable model
    \end{itemize}
  \end{itemize}
\end{frame}
%
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../main"
%%% End:
